---
title: "Google_Analytics_Cycle_Case_Study"
author: "Carlos_Rivera"
date: "2022-09-01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The first step when running a code in R is to install the necessary packages. In this case we will be using the tidyverse package. To install the latest version of this package we run the chunk below:

```{r tidyverse_install}
install.packages("tidyverse",repos = "http://cran.us.r-project.org")
```

We then load the tidyverse package

```{r tidyverse_load}
library("tidyverse")
```

## Data Import

We will then need to import the data we have calculated in SQL we can do this with the read_csv() function

```{r data_import}
ride_information <-read.csv("https://www.dropbox.com/s/3agtk4eam3oqtn8/ride_information.csv?dl=1", header=TRUE, stringsAsFactors=FALSE)
```

We then print the data to check on the data types

```{r}
print(ride_information)
```
As we can see the ride_length value is a chr type. We need to change the data type to a period format for that we will need to install the lubridate package. We do that with the chunk below

```{r}
install.packages("lubridate",repos = "http://cran.us.r-project.org")
```
We then run the package

```{r}
library("lubridate")
```

We will then use the hms() function in lubridate. This changes the data_type of ride_length to the period data type:


```{r}
ride_information$ride_length<- hms(ride_information$ride_length)
```
We then print the data again to confirm our results

```{r}
print(ride_information)
```

We can confirm that the ride_length column is now on a period data type. We can now proceed with our analysis

## Data Graphing
For our analysis we will first graph the number of rides per day. Regardless of the user type 
```{r}
ggplot(data =ride_information, mapping = aes(x=day_of_the_week))+ geom_bar()+labs(title = "Number of Rides per Day",x="Day of the Week",y="Total Rides")

```

We will then create a box plot of the data for each user type. This will help us see if there are any outliers in the data

```{r}
ggplot(data =ride_information, mapping = aes(y=ride_length))+ geom_boxplot()+ facet_wrap(~member_casual)+labs(title = "Ride Length per User Type Boxplot",y="Ride Length")
```

We will then look the the number of trips for each day divided by the user type: member or casual

```{r}
ggplot(data =ride_information, mapping = aes(x=day_of_the_week))+ geom_bar()+ facet_wrap(~member_casual)+labs(title = "Number of Rides per Day",x="Day of the Week",y="Total Rides")+theme(axis.text.x = element_text(size = 10, angle = 45,hjust=1))
```

We will then look the total ride time by day divided by user type: member or casual


```{r}
ggplot(data =ride_information, mapping = aes(x=day_of_the_week , y=ride_length))+ geom_histogram(stat = "identity")+ facet_wrap(~member_casual)+theme(axis.text.x = element_text(size = 10, angle = 45,hjust=1))+labs(title = "Number of Rides per Day by User Type",x="Day of the Week",y="Total Rides")
```

