---
title: "UFO_R_Markdown"
author: "Carlos"
date: "2022-09-06"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The first step when running a code in R is to install the necessary packages. In this case we will be using the tidyverse package. To install the latest version of this package we run the chunk below:

```{r tidyverse_install}
install.packages("tidyverse",repos = "http://cran.us.r-project.org")
```

We then load the tidyverse package

```{r tidyverse_load}
library("tidyverse")
```

## Data Import

We will then need to import the data we have calculated in SQL we can do this with the read_csv() function

```{r data_import}
observations_per_country <-read.csv("https://raw.githubusercontent.com/Carly1269/PortfolioProjects/main/UFO_Sightings_Project/UFO_Sightings_SQL_Export/Observations_Per_Country.csv", header=TRUE, stringsAsFactors=FALSE)

observations_per_hour_of_the_day <-read.csv("https://raw.githubusercontent.com/Carly1269/PortfolioProjects/main/UFO_Sightings_Project/UFO_Sightings_SQL_Export/Observations_Per_Hour_of_the_Day.csv", header=TRUE, stringsAsFactors=FALSE)

observations_per_state <-read.csv("https://raw.githubusercontent.com/Carly1269/PortfolioProjects/main/UFO_Sightings_Project/UFO_Sightings_SQL_Export/Observations_Per_State.csv", header=TRUE, stringsAsFactors=FALSE)

observations_per_year <-read.csv("https://raw.githubusercontent.com/Carly1269/PortfolioProjects/main/UFO_Sightings_Project/UFO_Sightings_SQL_Export/Observations_Per_Year.csv", header=TRUE, stringsAsFactors=FALSE)


```
We then print the data to check on the data types

```{r data print}
print(observations_per_country)
print(observations_per_hour_of_the_day)
print(observations_per_state)
print(observations_per_year)
```
We can see that the data types are correct. We will then proceed with our analysis
## Data Graphing
We will first graph the total number observations per hour of the day
```{r graph1}
ggplot(data =observations_per_hour_of_the_day, mapping = aes(x=hour_observed, y=number_of_observations))+ geom_bar(stat = "identity")+labs(title = "Number of Observations per Hour",x="Hour of the day",y="Total Observations")
```

As we can see most observations happen during the night time.

We will then graph the data of the total number of observations per state:

```{r graph2}
ggplot(data =observations_per_state, mapping = aes(x=stateid, y=sate_sighting_count))+ geom_bar(stat = "identity")+labs(title = "Number of Observations per State",x="State",y="Total Observations")
```

We can see that the data varies a lot. To visualize it better we will order the states from the most number of observations to the least. We will also tilt the state ids for better visualization


```{r graph3}
ggplot(data =observations_per_state, mapping = aes(x=reorder(stateid,-sate_sighting_count), y=sate_sighting_count))+ geom_bar(stat = "identity")+theme(axis.text.x = element_text(size = 10, angle = 90))+labs(title = "Number of Observations per State",x="State",y="Total Observations")
```

We can see that the state of California has the most number of observations. Followed by the state of Washington


We will then graph the total number of observations per year
```{r graph4}
ggplot(data =observations_per_year, mapping = aes(x=year_observed, y=number_of_observations))+ geom_bar(stat = "identity")+labs(title = "Number of Observations per Year",x="Year",y="Total Observations")
```

The graph is really hard to visualize since we have observations from thousands of years in the past. We will zoom into our graph to better see our data

```{r graph5}
ggplot(data =observations_per_year, mapping = aes(x=year_observed, y=number_of_observations))+ geom_bar(stat = "identity")+coord_cartesian(xlim = c(1930,2021))+labs(title = "Number of Observations per Year",x="Year",y="Total Observations")
```

